### 2016-05-25 R/ITHIM.Rmd
Update to ITHIM.Rmd
Introduced getQuintiles into the instanciation of the ITHIM model

## Integrated Transport and Health Impacts Model (ITHIM)

This document will eventually serve as a compendium to the R package
_ITHIM_.  It will describe how to use the package to implement the
ITHIM model, as well as a detailed description of the model itself.

@@

```{r date}
date()
```

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("ITHIM")
```

## R Implementation

```{r instantiate}
ITHIM <- list(parameters = parList <- createParameterList(), means = computeMeanMatrices(parList))
```
Then we compute quintiles for active transport time.
```{r quints}
ITHIM <- within(ITHIM, {
quintilesActiveTransportTime <- computeQuintiles(means$meanActiveTransportTime, means$sdActiveTransportTime)
})
```

Then the METs by walking and cycling.
```{r quintMETs}
ITHIM <- within(ITHIM, {
  quintWalkingTime = list(M = quintilesActiveTransportTime[["M"]] * (1-means$propTimeCycling[,"M"]), F = quintilesActiveTransportTime[["F"]] * (1-means$propTimeCycling[,"F"]))
  quintCyclingTime = list(M = quintilesActiveTransportTime[["M"]] * (means$propTimeCycling[,"M"]), F = quintilesActiveTransportTime[["F"]] * (means$propTimeCycling[,"F"]))
  quintWalkingMET = list(M = means$meanWalkMET[,"M"]*quintWalkingTime[["M"]]/60, F = means$meanWalkMET[,"F"]*quintWalkingTime[["F"]]/60)
  quintCyclingMET = list(M = means$meanCycleMET[,"M"]*quintCyclingTime[["M"]]/60, F = means$meanCycleMET[,"F"]*quintCyclingTime[["F"]]/60)
})
```

And the METs for active travel.
```{r totalTravelMETS}
ITHIM <- within(ITHIM, {
quintTotalTravelMET = list(M = quintWalkingMET[["M"]] + quintCyclingMET[["M"]], F = quintWalkingMET[["F"]] + quintCyclingMET[["F"]])
})
```
Now we print all of the parameters and results.
```{r ITHIM}
names(ITHIM)
```
### Example
To run the example contained in the _ITHIM_ package run the following.

```{r package}
library("ITHIM")
example("ITHIM-package")
```

```{r plot1}
D <- melt(ITHIM$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

```{r plot2}
D <- melt(ITHIM$parameters$Rwt, c("age","sex"), value.name = "rhowt")
p <- ggplot(D, aes(age,  rhowt)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

## Archive
### Active Transport Estimates (Speed and Distance by Transport Mode)
These data were ripped out of the EXCEL workbook and vary per scenario.
```{r transportData, eval = FALSE, echo = FALSE}

>>>>

# Integrated Transport and Health Impacts Model

## R Package _ITHIM_
This document will eventually serve as a compendium to the R package
_ITHIM_.  It will describe how to use the package to implement the
ITHIM model, as well as a detailed description of the model itself.

@@

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install_github("syounkin/ITHIM")
library("ITHIM")
date()
```

### Instanciation

```{r instantiate}
ITHIM <- list(
  parameters = parameters <- createParameterList(),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```

```{r ITHIM}
names(ITHIM)
```

For help run the following.
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```

### Example
To run the example contained in the _ITHIM_ package run the following.

```{r package, eval = FALSE}
example("ITHIM-package")
```
### Figures

```{r plot1, echo = FALSE}
D <- melt(ITHIM$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

```{r plot2, echo = FALSE}
D <- melt(ITHIM$parameters$Rwt, c("age","sex"), value.name = "rhowt")
p <- ggplot(D, aes(age,  rhowt)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

# Code Graveyard

### Active Transport Estimates (Speed and Distance by Transport Mode)
These data were ripped out of the EXCEL workbook and vary per scenario.
```{r transportData, eval = FALSE, echo = FALSE}
